\item
Consider the stochastic system
\begin{align}
    \label{eq:1}
    Y(k) - 0.5 Y(k-1) = W(k) - 0.3 W(k-1)
\end{align}
where $W(k)$ is a wide sense stationary (WSS) zero mean white random sequence with unit variance, i.e.
\begin{align*}
    m_{_W} = 0 \hspace{2em} \Lambda_{_{WW}}(l)  = E\{W(k+l)W(k)\} = \delta(l)
\end{align*}
and $\delta(l)$ is the unit pulse function. In this problem, we will compare the theoretical value of the relevant covariances with empirical estimates of those quantities computed using MATLAB.
\footnote{Since MATLAB requires initial conditions to perform time simulations, the output of the system given by Eq.~\eqref{eq:1} will not, strictly speaking be WSS. However, if the length of the sample sequence is taken to be sufficiently long, the relevant quantities will be approximately given by time averages.}

\begin{enumerate}

\item
Do a matlab simulation of the response of this system for one sample sequence $w(k)$ :

\begin{enumerate}
    \item
    Generate the sample sequence $w(k)$ using {\tt w = randn(N,1); }, where {\tt N} is a large number (e.g. 5000).

    \item
    Generate the sample output sequence $y(k)$ using

    \begin{center}
        \verb|[y,k] = lsim(sys1,w,k);|
    \end{center}
    Notice that the vector {\tt k} must be defined.

    \item
    Generate and plot the the estimates of the covariances and cross-covariances $\Lambda_{WW}(j)$, $\Lambda_{WY}(j)$,  $\Lambda_{YW}(j)$, $\Lambda_{YY}(j)$, for $j = \{-10,\, -9,\, \cdots ,0,\, \cdots \,10\}$ using the matlab command {\tt xcov}, e.g.\

    \begin{center}
        \verb|cov_wy = xcov(w,y,10,'coeff');|
    \end{center}
    Read the help on  {\tt xcov}  to understand what the argument {\tt 'coeff'} does.
    \footnote{The MATLAB function {\tt xcov} is part of the signal processing toolbox. Those of you who do not have access to this toolbox can use a similar function that can be downloaded from the ME233 bSpace website.}
\end{enumerate}

\item
Determine the cross-covariance (cross-correlation) function
\begin{align*}
    \Lambda_{YW}(l) = E\{Y(k+l)W(k)\}
\end{align*}
and $\hat{\Lambda}_{YW}(z) = \sum_{l=-\infty}^{\infty} z^{-l} \Lambda_{YW}(l)$. Plot $\Lambda_{YW}(l)$ for $l = \{-10,\, -9,\, \cdots ,0,\, \cdots \,10\}$ and compare your results with those empirically obtained using MATLAB. Notice that $\Lambda_{YW}(l)$ is a casual sequence, i.e. $\Lambda_{YW}(l) = 0$ for $ l < 0$ and all the poles of $\hat{\Lambda}_{YW}(z)$ will be inside the unit circle.

\item
Determine the cross-covariance (cross-correlation) function
\begin{align*}
    \Lambda_{WY}(l) = E\{W(k+l)Y(k)\}
\end{align*}
and $\hat{\Lambda}_{WY}(z) = \sum_{l=-\infty}^{\infty} z^{-l} \Lambda_{WY}(l)$. Plot $\Lambda_{WY}(l)$ for $l = \{-10,\, -9,\, \cdots ,0,\, \cdots \,10\}$ and compare your results with those empirically obtained using MATLAB. Notice that $\Lambda_{WY}(l)$ is an anti-casual sequence, i.e. $\Lambda_{WY}(l) = 0$ for $ l > 0$ and all the poles of $\hat{\Lambda}_{WY}(z)$ will be outside the unit circle.

%\item
%Determine the spectral density function
%\begin{align*}
%    \Phi_{_{YY}}(\omega) = \Lambda_{_{YY}}(z)|_{z = e^{j\omega}}
%\end{align*}
%of the random sequence $Y(k)$ and plot $\Phi_{_{YY}}(\omega)$ as a function of $\omega \in [-\pi,\,\pi]$.

\item
Determine the auto-covariance (auto-correlation) function
\begin{align*}
    \Lambda_{YY}(l) = E\{Y(k+l)Y(k)\}
\end{align*}
and $\hat{\Lambda}_{YY}(z) = \sum_{l=-\infty}^{\infty} z^{-l} \Lambda_{YY}(l)$. Plot $\Lambda_{YY}(l)$ for $l = \{-10,\, -9,\, \cdots ,0,\, \cdots \,10\}$ and compare your results with those empirically obtained using MATLAB. Notice that $\hat{\Lambda}_{YY}(z)$ will have poles both outside and inside the unit circle.

\textbf{Hint:} After finding $\hat{\Lambda}_{YY}(z)$, find its inverse Z-transform using the results of problem 1.

\item
Compute $\Lambda_{_{YW}}(0)$ utilizing Eq.~\eqref{eq:1}.

\textbf{Hint:} Multiply both sides of Eq.~\eqref{eq:1} by $W(k)$ and take expectations.

\item
Compute $\Lambda_{_{YW}}(1)$ utilizing Eq.~\eqref{eq:1}.

\textbf{Hint:} Multiply both sides of Eq.~\eqref{eq:1} by $W(k-1)$ and take expectations.


\item
Compute $\Lambda_{_{YY}}(0)$ utilizing equation \eqref{eq:1}.

\textbf{Hint:} From Eq.~\eqref{eq:1} we have
\begin{align}
    \label{eq:2}
    Y(k) =  0.5 Y(k-1)+ W(k) - 0.3 W(k-1) \; .
\end{align}
Square both sides of Eq.~\eqref{eq:2} and take expectations.

\end{enumerate}


